\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-28 paper.tex
new
?

\section{MCMC-based Informed Sampling}
The informed set induces a probability distribution $\Pinf$. 
Here, points in \Cinf are distributed uniformly
while 
the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
Our goal is to efficiently produce samples (approximately) from \Pinf.

\os{connect previous par}

In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
We start  by randomly sampling a state~$x_\text{rand} \in \calX$ and use it
to produces a sample~$x_\text{boundary} \in \partial\Cinf$ which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad}).
This is done by applying Newton-Raphson method~\cite{RT06}.
We then use~$x_\text{boundary}$ to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}). Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
For a visualization of the approach, see Fig.~\ref{fig:alg}.

@@

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
		\STATE $x_{\text{boundary}} \leftarrow
		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$
		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
		\FOR {$i = 1$ to $N$}
			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
			\STATE \textbf{output} $x_{i}$
		\ENDFOR

@@

\dy{should the ``return'' in Algorithm 1 \ref{alg:mcmc_informed_sampling} be ``yield"?}

@@

>>>>

\section{MCMC-based Informed Sampling}
In this section we describe our approach to efficiently produce samples in the informed set~\Cinf given a specific cost~$c_{\text{best}}$.
Our algorithm (see Alg.~\ref{alg:mcmc_informed_sampling}) starts by randomly sampling a state~$x_\text{rand} \in \calX$ (line~1).
This sample is used to produces a 
sample~$x_0 \in \partial\Cinf$ 
%sample~$x_\text{boundary} \in \partial\Cinf$ 
which lies (approximately) on the boundary of the informed set (Sec.~\ref{subsec:grad})by applying Newton-Raphson method~\cite{RT06} (line~2).
Finally,~$x_0$ 
%use~$x_\text{boundary}$ 
is used (lines~3-5)
to initialize an MCMC algorithm which produces a series of samples within \Cinf (Sec.~\ref{subsec:mcmc}). Specifically, we chose to use HMC due to its favourable properties (see Sec.~\ref{sec:intro}). 
For a visualization of the approach, see Fig.~\ref{fig:alg}.

We apply MCMC by using the cost function to define a probability distribution \Pinf.
Specifically, points in \Cinf are distributed uniformly
while 
the probability of sampling any configuration $x \in \calX \setminus \Cinf$ is zero.
The MCMC algorithm will allow us to  efficiently produce samples (approximately) from \Pinf.

@@

\begin{algorithm}[t]
	\begin{algorithmic}[1]
		\STATE $x_{\text{rand}} \leftarrow \texttt{sample\_uniform(\calX)}$
%		\STATE $x_{\text{boundary}} 
		\STATE $x_{0} 
		 \leftarrow
		 \texttt{newton\_raphson}(x_{\text{rand}}, c_{\text{best}})$
%		\STATE $x_{0} \leftarrow x_{\text{boundary}}$
		\FOR {$i = 1$ to $N$}
			\STATE $x_{i} \leftarrow \texttt{MCMC} (x_{i-1}, c_{\text{best}})$
			\STATE \textbf{output} $x_{i}$
		\ENDFOR

@@

@@

\begin{figure}[tb]
	\centering
	\includegraphics[height = 4.5cm ]{fig/sampling_efficiency.pdf}
	\caption{
		\captionstyle
		Compare time efficiency of generating 1000 samplings.
	}
	\label{fig:compare_time_efficiency}
\end{figure}
